Compiling refinement types to dependent types

### 2020-07-14 tex/paper.tex
We indeed are going to prove WTP by induction on the typing derivation
Some stub text prior to the definition of the surface language

@@

\begin{theorem}[Well-typedness preservation]
  For any well-typed surface language term $\nonterm{es}$,
  the result of the translation $\tranterm(\nonterm{es})$ is ``equivalently'' typeable in the core language:
  \[
    \nonterm G \vdash \nonterm{es} : \nonterm{ts} \implies \tranctx(\nonterm G) \vdash \tranterm(\nonterm{es}) : \tranty(\nonterm{ts})
  \]
\end{theorem}
\begin{proof}
\end{proof}

>>>>

Our surface language is based on simply typed lambda calculus.
Refinements over the types are, of course, the most important extension.
The other ones are:
\begin{itemize}
  \item dependent arrow types, to allow subsequent refinements refer preceding arguments,
  \item limited form of algebraic data types and dependent pattern matching,
    to illustrate reasoning about those widely used constructs.
\end{itemize}

@@

\begin{theorem}[Well-typedness preservation]
  For any well-typed surface language term $\nonterm{es}$,
  the result of the translation $\tranterm(\nonterm{es})$ is ``equivalently'' typeable in the core language:
  \[
    \nonterm G \vdash \nonterm{es} : \nonterm{ts} \implies \tranctx(\nonterm G) \vdash \tranterm(\nonterm{es}) : \tranty(\nonterm{ts})
  \]
\end{theorem}
\begin{proof}
  We prove this by induction on the derivation of the typeability of $\nonterm{es}$.
  In particular, we consider the last typing rule used:
\end{proof}
